---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figure/"
)
```

[![Travis-CI Build Status](https://travis-ci.org/earowang/rwalkr.svg?branch=master)](https://travis-ci.org/earowang/rwalkr)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/rwalkr)](https://cran.r-project.org/package=rwalkr)

# rwalkr

The goal of **rwalkr** is to provide API to the pedestrian data from the City of Melbourne in tidy data form.

## Installation

You could install the stable version from CRAN:

```{r, eval = FALSE}
install.packages("rwalkr")
```

You could install the development version from Github using:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("earowang/rwalkr")
```

## Usage

Currently there is only one function in the package, `walk_melb()`. The starting and ending dates inform which period to be scraped.

```{r data}
library(rwalkr)
start_date <- as.Date("2017-07-01")
end_date <- start_date + 6L
ped <- walk_melb(from = start_date, to = end_date)
head(ped)
```

```{r plot, fig.height = 4}
library(ggplot2)
ggplot(data = subset(ped, Sensor == "Melbourne Central")) +
  geom_line(aes(x = Date_Time, y = Count))
```

## Acknowledgements

Thanks to Stuart Lee (@sa-lee) for inspiring this package.
